A studyforrest extension, an annotation of words and phonemes in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-04-15 paper/main.tex
More comments on the annotation procedure

\section*{Materials and methods}
\subsection*{Stimulus}
% References sind vom Anno-Paper in die .bib-Datei übernommen worden; die
% “hardcoded” Zitationen sind aber noch im laufenden Text.
We annotated speech in stimuli built from the motion picture ``Forrest Gump'' as
used in two previous studies: an audio-visual movie
\citep{hanke2016simultaneous}, and its temporally aligned audio-description
\citep{hanke2014audiomovie}. For the movie stimulus, we used the audio track of
the German DVD release (Paramount Home Entertainment, Germany, 2002; PAL video,
DE103519SV)\citep{ForrestGumpDVD}. For the audio-only stimulus, we used the
movie's audio-description that was broadcast as an additional audio track for
visually impaired listeners on Swiss public television (Koop, Michalski,
Beckmann, Meinhardt \& Benecke, produced by Bayrischer Rundfunk,
2009)\citep{ForrestGumpGermanAD}. The plot of the movie is already carried by an
off-screen voice of the main character Forrest Gump. In the largely identical audio-description, a male narrator additionally describes essential aspects of the visual scenery when there is no off-screen voice, dialog, or other relevant auditory content
\subsection*{Annotation procedure}
% wo kommen die "preliminaries transcriptions" her?
% Die "most basic" Datei, die das Dataset enthält ist der Merge aus Diaolog, Narrator & Non-Speech-Annotation
Preliminary, orthographic transcriptions of dialogues (german\_dialog.csv),
non-speech vocalizations (e.g. laughing or groaning;
non\_speech\_vocalization.json), and the audio-description's narrator
(german\_audio\_description.csv) were merged and converted to Praat's
\citep{boersma2019praat} .TextGrid format (
\href{www.fon.hum.uva.nl/praat}{fon.hum.uva.nl/praat}). The merged transcription
containing one onset and offset for usually a couple of sentences was opened
along (the audio file of) the audio-description in Praat v6.0.22 for manual
improvements: In several passes, the approximate temporal onsets and offsets
were corrected. Intervals containing several sentences were split into intervals
containing only one sentence. When two or more persons were speaking
simultaneously the less dominant (background) voice was dropped. Low volume
background speech (especially occurring during music or continuous environmental
noise) or low volume non-speech vocalizations that are difficult to recognize by
a regular audience were dropped, too.

% Alignment preparations
We used the Montreal Forced Aligner v1.0.1
\href{montrealcorpustools.github.io/Montreal-Forced-Aligner}{montrealcorpustools.github.io/Montreal-Forced-Aligner}\citep{mcauliffe2017montreal};to
algorithmically identify the onset and offset of each word and phoneme embedded
in the transcribed sentences. To enable the aligner to look up the pronunciation
of every word, we chose a German pronunciation dictionary
\href{https://raw.githubusercontent.com/prosodylab/prosodylab.dictionaries/master/de.dict}{raw.githubusercontent.com/prosodylab/prosodylab.dictionaries/master/de.dict}
provided by Prosodylab (\href{http://prosodylab.org}{prosodylab.org}) that uses
the Prosodylab PhoneSet. The dictionary was manually updated with movie-specific
German words. The pronunciation of English words occurring in the otherwise
German audio track was taken from an English pronunciation dictionary
(\href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org/mfa/dictionaries/english.dict} that uses the ARPAbet PhoneSet.

% Alignment
% Nicht erwähnt: Wenn die Korrektur der Phoneme unmöglich war, habe ich einfach
% die Event-Borders zwischen den Phonemen herausgenommen. Wortbeginn und Wortende stimmen dann mit einem neuen, "künstlich-großen Phoneme" überein.
% Das "Groß-Phonem" enthält dann ohne Grenzen zwischen den tatsächlichen Phonemen des Wortes alle Phoneme des Wortes ("es ist kompliziert zu erklären, aber im Grunde ganz einfach).
% kommt selten vor, ist im Grunde "noise" und ist in der Anno sofort als solches zu erkennen.
The audio file was converted from .FLAC to .WAV via ffmpeg v4.1.4
(\href{www.ffmpeg.org}{ffmpeg.org}) to meet the aligner's requirements. This
.WAV file, the transcription of sentences, and the updated dictionary were
submitted to the aligner that first trained an acoustic model on the data and
then performed the alignment. In a first step, the resulting .TextGrid file that
contains onsets and offsets of words and phonemes was opened in Praat to check
and correct the automatic alignment. In several passes, words [and their
corresponding phonemes] on which the automatic alignment performed moderately
were corrected. Some (low volume) sentences that are spoken in continuously
noisy settings (pursuit, battle, hurricane, demonstration/rally, disco) were
removed due to poor overall alignment performance. In a second step, the
complete sentences of the orthographic transcription were copied into the
annotation (s. table \ref{tab:overview} for an overview of the annotation's content). In a third step, the name of the speaker was added for every sentence (s. table \ref{tab:speakers} for the most often occurring speakers).
During every new step results from all previous steps were checked again for errors and corrected.

>>>>

\todo[inline]{this work seems to improve/replace previous work (in part), it is important to state that clearly and identify which pieces are involved}

\section*{Materials and methods}
\subsection*{Stimulus}
% References sind vom Anno-Paper in die .bib-Datei übernommen worden; die
% “hardcoded” Zitationen sind aber noch im laufenden Text.
We annotated speech in stimuli built from the motion picture ``Forrest Gump'' as
used in two previous studies: an audio-visual movie
\citep{hanke2016simultaneous}, and its temporally aligned audio-description
\citep{hanke2014audiomovie}. For the movie stimulus, we used the audio track of
the German DVD release (Paramount Home Entertainment, Germany, 2002; PAL video,
DE103519SV)\citep{ForrestGumpDVD}. For the audio-only stimulus, we used the
movie's audio-description that was broadcast as an additional audio track for
visually impaired listeners on Swiss public television (Koop, Michalski,
Beckmann, Meinhardt \& Benecke, produced by Bayrischer Rundfunk,
2009)\citep{ForrestGumpGermanAD}. The plot of the movie is already carried by an
off-screen voice of the main character Forrest Gump. In the largely identical audio-description, a male narrator additionally describes essential aspects of the visual scenery when there is no off-screen voice, dialog, or other relevant auditory content

\subsection*{Annotation procedure}
% wo kommen die "preliminaries transcriptions" her?
% Die "most basic" Datei, die das Dataset enthält ist der Merge aus Diaolog, Narrator & Non-Speech-Annotation
Preliminary, orthographic transcriptions of dialogues (\texttt{german\_dialog.csv})\todo{filenames should have some text markup. I did this example, please apply to other locations as well},
non-speech vocalizations (e.g. laughing or groaning;
non\_speech\_vocalization.json), and the audio-description's narrator
(german\_audio\_description.csv)\todo{where were those from? citation missing} were merged and converted to Praat's
\citep{boersma2019praat} TextGrid format (
\href{www.fon.hum.uva.nl/praat}{fon.hum.uva.nl/praat}). The merged transcription
containing one onset and offset for usually a couple of sentences was opened
along (the audio file of) the audio-description in Praat v6.0.22 for manual
improvements\todo{in general process information is not relevant: of course you need to open a file to work with it. The Q is what you did to it, why, and how exactly. So instead of "was opened along (the audio file of) the audio-description in Praat v6.0.22", better "was edited in Praat v6.0.22 for manual validation against the original audio"}: In several passes\todo{why several passes?}, the approximate temporal onsets and offsets
were corrected. Intervals containing several sentences were split into intervals
containing only one sentence. When two or more persons were speaking
simultaneously the less dominant (background) voice was dropped. Low volume
background speech (especially occurring during music or continuous environmental
noise) or low volume non-speech vocalizations that are difficult to recognize by
a regular audience\todo{what is a regular audience? without neurological disorders ;-)} were dropped, too.

% Alignment preparations
We used the Montreal Forced Aligner v1.0.1 
\href{montrealcorpustools.github.io/Montreal-Forced-Aligner}{montrealcorpustools.github.io/Montreal-Forced-Aligner}\citep{mcauliffe2017montreal}\todo{we need a consistent way of citing software. I think it is overkill to have a reference, plus a URL, plus a version in the main text. Either everything in the reference, or (maybe) just name+version in the text};to
algorithmically identify the onset and offset of each word and phoneme embedded
in the transcribed sentences. To enable the aligner to look up the pronunciation
of every word, we chose a German pronunciation dictionary
\href{https://raw.githubusercontent.com/prosodylab/prosodylab.dictionaries/master/de.dict}{raw.githubusercontent.com/prosodylab/prosodylab.dictionaries/master/de.dict}
provided by Prosodylab (\href{http://prosodylab.org}{prosodylab.org}) that uses
the Prosodylab PhoneSet\todo{same here, use a proper bibtex reference}. The dictionary was manually updated with movie-specific
German words\todo{which words, how determined, why?}. The pronunciation of English words occurring in the otherwise
German audio track was taken from an English pronunciation dictionary
(\href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org/mfa/dictionaries/english.dict} that uses the ARPAbet PhoneSet\todo{It would help a non-expert like me to understand why a PhoneSet is important for this annotation, sounds like a jargon}.

% Alignment
% Nicht erwähnt: Wenn die Korrektur der Phoneme unmöglich war, habe ich einfach
% die Event-Borders zwischen den Phonemen herausgenommen. Wortbeginn und Wortende stimmen dann mit einem neuen, "künstlich-großen Phoneme" überein.
% Das "Groß-Phonem" enthält dann ohne Grenzen zwischen den tatsächlichen Phonemen des Wortes alle Phoneme des Wortes ("es ist kompliziert zu erklären, aber im Grunde ganz einfach).
% kommt selten vor, ist im Grunde "noise" und ist in der Anno sofort als solches zu erkennen.
The audio file was converted from .FLAC to .WAV\todo{Better WAV not .WAV, likewise for others} via ffmpeg v4.1.4
(\href{www.ffmpeg.org}{ffmpeg.org}) to meet the aligner's requirements. This
.WAV file, the transcription of sentences, and the updated dictionary were
submitted to the aligner that first trained an acoustic model on the data and
then performed the alignment. In a first step, the resulting .TextGrid file that
contains onsets and offsets of words and phonemes was opened in Praat to check
and correct the automatic alignment. In several passes, words [and their
corresponding phonemes] on which the automatic alignment performed moderately
were corrected. Some (low volume) sentences that are spoken in continuously
noisy settings (pursuit, battle, hurricane, demonstration/rally, disco) were
removed due to poor overall alignment performance. In a second step, the
complete sentences of the orthographic transcription were copied into the
annotation (s. table \ref{tab:overview} for an overview of the annotation's content). In a third step, the name of the speaker was added for every sentence (s. table \ref{tab:speakers} for the most often occurring speakers).
During every new step results from all previous steps were checked again for errors and corrected.
